Identifiers for Iterative Forecasting

### 2021-12-10 paper/paper.Rmd
WIP

**Managing storage**:

The tsv-backed registry uses a simple tab-separated-value list to match URLs or filepaths to a content identifier.
By default, this registry computes and stores a `sha256` checksum, which can be configured using 
the environmental variable "CONTENTID_ALGOS" (which also recognizes `md5`, `sha1`, `sha384` and `sha512` checksums). 
Entries can be added to the `tsv` registry using the `register()` function.  
By default, `register()` will also attempt to register URLs with any 
hash-archive type registries, discussed below. Here we enforce a tsv-only registry, 
specifying the creation of a tsv file in the current working directory rather than the default location.

@@

It is possible to register a local filepath instead of a URL, though these sources will not be portable.
Extracting sources from a tsv-backed registry is quite fast owing to the performance of `vroom`.  
However, users maintaining local registries with millions of entries will benefit from the much greater performance of LMDB, provided by the `thor` package.

```{r}
# LMDB is a database handle, not a path
db <- default_lmdb()
id <- register("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542",
               db)
sources(id, db)
```

>>>>

**Managing content storage**: Storing data by content-address ensures that our files are not accidentally over-written by other content,
and provides the most minimal and fastest data registry and store.
However, because hashes are opaque, without a metadata record it is easy to lose track of what objects are in the content store.
Meanwhile, because every unique version of a file is preserved, it is also possible to fill up available storage very quickly.
Therefore, users are encouraged to treat the local content store as temporary cache only that works in conjunction with data
that can be accessed using another registry type, rather than as the sole long-term storage location for data.
As such, to manage file size, it may be helpful to purge this storage location from time to time when storage grows to large.
The helper utility, `purge_cache()`, does exactly that, removing the oldest files in the content store until the cache is 
reduced to within a specified threshold size, or any files over a maximum age.

**TSV-backed registry**.
The tsv-backed registry uses a simple tab-separated-value list to match URLs or filepaths to a content identifier.
By default, this registry computes and stores a `sha256` checksum, which can be configured using 
the environmental variable "CONTENTID_ALGOS" (which also recognizes `md5`, `sha1`, `sha384` and `sha512` checksums). 
Entries can be added to the `tsv` registry using the `register()` function.  
By default, `register()` will also attempt to register URLs with any 
hash-archive type registries, discussed below. Here we enforce a tsv-only registry, 
specifying the creation of a tsv file in the current working directory rather than the default location.

@@

Note that this registry is not also a store -- the tsv file preserves only the URL or path at which the source was found,
not the data itself. 
If the file is moved to another local path or URL, `resolve()` will detect the failure and try the next available source, if any.  
It is possible to register a local filepath instead of a URL, though these sources will not be portable.
Extracting sources from a tsv-backed registry is quite fast owing to the performance of `vroom`.  
However, users maintaining local registries with millions of entries will benefit from the much greater performance of LMDB, provided by the `thor` package.

**LMDB-backed registry**

The LMDB-backed registry is the only one not activated by default.
It is a special-case registry that can be useful for users seeking to manage a huge number of individual objects by contentid, typically without calls to remote services.
As such, it will typically be used alone, rather than simultaneously with (generally much slower) calls to other registries.

```{r}
# LMDB is a database handle, not a path
db <- default_lmdb()
id <- register("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/ess-dive-457358fdc81d3a5-20180726T203952542",
               registries = db)
sources(id, db)
```
